---
title: "Leaflet Dygraph Vignette"
resource_files:
- leafletvignetteDataGrab.R
- sourceData.RDat
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    source_code: embed
    vertical_layout: scroll
---

```{r setup, include=FALSE}
# Load packages and initialize data here
library(flexdashboard)
library(scales)
library(dygraphs)
library(leaflet)
library(macrodata)
library(dplyr)
library(countrycode)
library(ggplot2)
library(plotly)
library(DT)

##load data
load('sourceData.RDat')

##create shading by GDP
pal <- colorNumeric(
  palette = "Blues",
  domain = countries$gdp_md_est
)

qpal <- colorQuantile("Blues", countries$gdp_md_est, n = 20)

##create popup country name and economic stage
popup <- paste0("<strong>Country: </strong>", 
                countries$name, 
                "<br><strong>Market Stage: </strong>", 
                countries$economy)

leaf_world <- leaflet(countries) %>%
  addProviderTiles("CartoDB.Positron") %>% 
  setView(lng =  90, lat =  15, zoom = 2) %>%
      addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = .7, color =
      ~qpal(gdp_md_est), layerId = ~name, popup = popup)

##build map of georgia shaded by county population

ga <- subset(counties, counties$STATEFP %in% c("13"))
ga <- ga[order(ga$NAME),]

##add population data to the ga spatial data frame
ga$POPULATION <- as.numeric(ga_counties_DF$`Population Estimate (as of July 1) - 2012`)


GApal <- colorNumeric(
  palette = "Blues",
  domain = ga$POPULATION
)

GApal <- colorQuantile("Blues", ga$POPULATION, n = 20)

GApopup <- paste0("<strong>County: </strong>", 
                ga$NAME, 
                "<br><strong>Population: </strong>", 
                ga$POPULATION)

leaf_georgia <- leaflet(ga) %>%
  addProviderTiles("CartoDB.Positron") %>%
      addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = .7, color =
      ~GApal(POPULATION), layerId = ~NAME, popup = GApopup)

##load up some gdp and population data
gdp2008 <- as.data.frame(countries$gdp_md_est)
rownames(gdp2008) <- countries$name
gdp2008$pop <- countries$pop_est
colnames(gdp2008) <- c("GDP", "Population")

```


World Map Time Series {data-orientation=rows}
=====================================

Sidebar {.sidebar}
-------------------------------------
  
```{r}

helpText("Select an economic time series.")

selectInput("indicatorselect2", "Choose an economic indicator", 
                          choices = c("GDP Per Capita", "GDP Per Capita Growth", 
                                      "Real Interest Rate", "Exchange Rate (2005 = 100)",
                                      "CPI", 
                                      "Labor Force Part. Rate - all", "Labor Force Part. Rate 
                                      - Women"))

```

Row {data-height=650}
-------------------------------------

### World Map

```{r, echo = FALSE}

  leafletOutput("map1")

  output$map1 <- renderLeaflet({
    leaf_world
  })
```

Row {.tabset .tabset-fade}
-------------------------------------

### Economic Time Series

```{r, echo = FALSE}

dygraphOutput("dygraph2")
  
   clickedCountry <- eventReactive(input$map1_shape_click, {
     return(input$map1_shape_click$id)
     })
   
   indicatorInput2 <- reactive({
     switch(input$indicatorselect2,
         "GDP Per Capita" = WorldGDPPerCapita,
         "GDP Per Capita Growth" = WorldGDPPerCapitaGrowth,
         "Real Interest Rate" = WorldRealInterestRate, 
         "Exchange Rate (2005 = 100)" = WorldExchangeRate, 
         "CPI" = WorldCPI, 
         "Labor Force Part. Rate - Women" = WorldFemaleLaborPartRate, 
         "Labor Force Part. Rate - all" = WorldTotalLaborPartRate)
})
   
   output$dygraph2 <- renderDygraph({
    
    ##get the economic indicator from the sidebar 
    indicator2<-indicatorInput2()
    
    ##turn the country clicked on into a country code
    code2<- countrycode(as.character(clickedCountry()), "country.name", "iso3c")
    
    dygraph(indicator2[, code2], main = clickedCountry()) %>%
      dyRangeSelector(height = 20) %>%
      dyShading(from = "2007-12-01", to = "2009-06-01", color = "#FFE6E6") %>% 
      dyEvent(x = "2008-09-15", label = "Fin Crisis", labelLoc =
      "top", color = "red")
      })
   
```


### Data Table Country Indicators

```{r}
renderDataTable({
    ##get the economic indicator from t
    indicator2<-indicatorInput2()
    
    ##turn the country clicked on into a country code
    code2<- countrycode(as.character(clickedCountry()), "country.name", "iso3c")
    
    countryData <- merge(WorldCPI[, code2], 
                         WorldExchangeRate[, code2],         
                         WorldGDPPerCapitaGrowth[, code2], 
                         WorldGDPPerCapita[, code2],
                         WorldRealInterestRate[, code2],
                         WorldTotalLaborPartRate[, code2],
                         WorldFemaleLaborPartRate[, code2])
    countryDataTable <- as.data.table(countryData)
    colnames(countryDataTable)<- c( "Date",
                                   "CPI", 
                                   "Exchange Rate", 
                                   "GDP per cap growth", 
                                   "GDP Growth",
                                   "Int. Rate", 
                                   "Labor Part.",
                                   "Fem. Lab. Part.")
    
    return(countryDataTable)
  })

```
 


Georgia Map {data-orientation=rows}
=====================================

Sidebar {.sidebar}
-------------------------------------
  
```{r}

helpText("Select an economic time series.")

selectInput("indicatorselect1", "Choose a time series", 
                          choices = c("Deposits", "Unemployment Rate", 
                                      "Average Mortgage Size"))

```

Row {data-height=650}
-------------------------------------

### Georgia Counties

```{r, echo = FALSE}

leafletOutput("map2")

  output$map2 <- renderLeaflet({
    leaf_georgia
  })

```

Row {data-height=350}
-------------------------------------

### Total Deposits over Time

```{r}
##get the county that was clicked on

dygraphOutput("dygraph3")

clickedCounty <- eventReactive(input$map2_shape_click, {
     return(input$map2_shape_click$id)
     })

output$dygraph3 <- renderDygraph({
dygraph(gaCounty_xts[, as.character(clickedCounty())], main = clickedCounty()) %>%
      dyRangeSelector(height = 20) %>%
  dyAxis(
    "y",
    label = "Deposits",
    valueFormatter = 'function(d){return d.toString().replace(/\\B(?=(\\d{3})+(?!\\d))/g, ",");}',
    axisLabelFormatter = 'function(d){return d.toString().replace(/\\B(?=(\\d{3})+(?!\\d))/g, ",");}',
    axisLabelFontSize = 10,
    axisLabelWidth = 70) %>% 
    dyShading(from = "2007-12-01", to = "2009-06-01", color = "#FFE6E6") %>% 
      dyEvent(x = "2008-09-15", label = "Fin Crisis", labelLoc =
      "top", color = "red")
      })
```

Linked Brushing {data-orientation=columns}
=====================================

Column {data-width=350}
-----------------------------------------------------------------------

### GDP v. Population {data-width=600}

```{r, echo=FALSE}
# Reactive that returns the whole dataset if there is no brush
selectedData <- reactive({
  data <- brushedPoints(gdp2008, input$plot1_brush)
  if (nrow(data) == 0)
    data <- gdp2008
  data
})

plotOutput("plot1", brush = brushOpts(id = "plot1_brush"))
output$plot1 <- renderPlot({
  ggplot(gdp2008, aes(Population, GDP)) + geom_point()
})

```

Column {data-width=350}
-----------------------------------------------------------------------

### Country Details

```{r}
renderTable({
  selectedData()
})
```

Notes {data-icon="fa-list"}
=====================================

### Thoughts and applications

- finance/investment management 

- banking: deposits/mortgage revenue by county, state 

- insurance: risk/claims by location

- epidemiology: health risks across regions

- public safety (Pittsburgh): crimes/captial by neighborhood

- non-profit: fundraising by state over time

- select two location for pairs data, such as cross-border trade

- multiple time series to move beyond data exploration to statistical inference

- reversing the reactivity: Leaflet reacts to the Dygraph input


